---
title: "Project Random Forest Trial 1"
author: "Nhi (Chelsea) Le"
date: "5/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> Creating the training and test sets

```{r}
load("data/sketches_test.rda")
load("data/sketches_train.rda")

library(tidymodels)

set.seed(123) 
sketches_split <- initial_split(sketches, strata = word) 

sketches_train <- training(sketches_split)
sketches_test <- testing(sketches_split)
```

> Creating the recipe: 

```{r}
sketches_rec <- recipe(word ~ ., data = sketches_train) %>% 
  update_role(id, new_role = "ID") 

sketches_prep <- prep(sketches_rec)
juiced <- juice(sketches_prep)
```

> Creating the tuning specifications

```{r}
tune_spec <- rand_forest(
  mtry = tune(), 
  trees = 1000, 
  min_n = tune()
) %>% 
  set_mode("classification") %>% 
  set_engine("ranger")
```

> Creating the workflow

```{r}
tune_wf <- workflow() %>% 
  add_recipe(sketches_rec) %>% 
  add_model(tune_spec)
```

> Creating a set of cross-validation resamples to use for tuning

```{r}
set.seed(234) 
sketches_folds <- vfold_cv(sketches_train)
```

> Training different models to see which ones turn out best. Using parallel processing to fasten things up (since different parts of the grid are independent). Choosing 20 grid points

```{r}
doParallel::registerDoParallel()

set.seed(345)
tune_res <- tune_grid(
  tune_wf, 
  resamples = sketches_folds, 
  grid = 20
)

tune_res
```

> Looking at min_n and mtry with regard to AUC

```{r}
library(tidyverse)
tune_res %>% 
  collect_metrics() %>% 
  filter(.metric == "roc_auc") %>% 
  select(mean, min_n, mtry) %>% 
  pivot_longer(min_n:mtry, 
               values_to = "value", 
               names_to = "parameter") %>% 
  ggplot(aes(value, mean, color = parameter)) + 
  geom_point(show.legend = FALSE, size = 2) + 
  facet_wrap(~parameter, scales = "free_x") + 
  labs(x = NULL, y = "AUC")
```
> It looks like lower values of mtry are good (below 400) and lower values of min_n are also good (below about 16). We can get a better handle on the hyperparameters by tuning one more time, this time using regular_grid(). Let’s set ranges of hyperparameters we want to try, based on the results from our initial tune. 

> Tuning the hyperparameters one more time using regular_grid(), setting the ranges of the hyperparameters based on the results from initial tune

```{r}
rf_grid <- grid_regular(
  mtry(range = c(0,400)), 
  min_n(range = c(0,16)), 
  levels = 5
)

rf_grid
```

> Tuning one more time in a more targetted way with the rf_grid we've just produced

```{r}
set.seed(456)

regular_res <- tune_grid(
  tune_wf, 
  resamples = sketches_folds, 
  grid = rf_grid
)

regular_res
```

> Looking at the results after this round of tuning

```{r}
regular_res %>% 
  collect_metrics() %>% 
  filter(.metric == "roc_auc") %>% 
  mutate(min_n = factor(min_n)) %>% 
  ggplot(aes(mtry, mean, color = min_n)) + 
  geom_line(alpha = 0.5, size = 1.5) + 
  geom_point() + 
  labs(y = "AUC")
```

> Selecting the best model, and updating our original model specification `tune_spec` to create our final model specification

```{r}
best_auc <- select_best(regular_res, "roc_auc") 

final_rf <- finalize_model(
  tune_spec, 
  best_auc
)

final_rf
```

> Exploring the best model

```{r}
library(vip)
library(ranger)

set_engine("ranger", importance = "permutation") %>% 
  fit(word ~ ., 
      data = juice(sketches_prep) %>% select(-id)) %>% 
  vip(geom = "point")
```

> Making a final workflow, then fitting one last time, using `last_fit()`, which fits the model on the entire training set and evaluates on the test set

```{r}
final_wf <- workflow() %>% 
  add_recipe(sketches_rec) %>% 
  add_model(final_rf) 

final_res <- final_wf %>% 
  last_fit(sketches_split) 

final_res %>% 
  collect_metrics()
```

```{r}
predictions_final_res <- final_res$.predictions %>% 
  as.data.frame()

write_csv(predictions_final_res, path = "final_res_predictions_on_fake_test_set.csv")
```

```{r}
final_res$.workflow
```


```{r}
load("data/sketches_test.rda")

final_rf
```
```{r}
library(randomForest)
load("data/sketches_test.rda")
load("data/sketches_train.rda")

final_res$.workflow

random_forest <- randomForest(word~., data = sketches[,-786], ntree = 1000, mtry = 28, nodesize = 4)

sketches_test$word <- predict(random_forest, newdata=sketches_test)
predictions_trial <- sketches_test %>%
  select(id, word) %>%
  rename(Id=id, Category=word)

write_csv(predictions_trial, path = "predictions_28_05_2020(2).csv")
```

```{r}
library(randomForest)
```

